### 2015-02-28 icfp15-servo/open.tex
Text cleanups

\paragraph{Incremental computation.} As mentioned in \secref{sec:browsers},
all modern browsers use some combination of dirty bit marking and incremental
recomputation heuristics to avoid reprocessing the full page when
the state is mutated.
Unfortunately, these heuristics are not only frequently the source of
performance differences between browsers, but they are also a source of
correctness bugs.
A library that provided a form of self adjusting computation suited to
incremental recomputation of only the visible part of the page, perhaps
like the work on Adapton~\cite{adapton}, seems like a promising
approach to addressing this problem.

>>>>

\paragraph{Incremental computation.} As mentioned in \secref{sec:browsers},
all modern browsers use some combination of dirty bit marking and incremental
recomputation heuristics to avoid reprocessing the full page when
a mutatation is performed.
Unfortunately, these heuristics are not only frequently the source of
performance differences between browsers, but they are also a source of
correctness bugs.
A library that provided a form of self adjusting computation suited to
incremental recomputation of only the visible part of the page, perhaps
based on the Adapton~\cite{adapton} approach, seems promising.
